---
title: "BA - data preparation - 2"
output: html_notebook
---

# Preparation of the chosen data sets

The chosen inputs are:
- CO2
- material footprint
- government debts
- foreign direct investment

The chosen outputs are
- life expectancy
- income
- mean years of schooling
- murder rate
- income share of lowest 20 percent


Both inputs and output data sets need to be adjusted according to the input oriented DEA. 
Inputs should be minimized, outputs should be maximized to achieve optimal results. Also, all data must be strictly positive.


```{r}
library(tidyverse) 

source("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/code/functions.R")
```

## Load data

```{r}
# Inputs:
material_footprint <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/material_footprint.csv",show_col_types = FALSE)
CO2 <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/CO2.csv",show_col_types = FALSE)
foreign_investment <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/foreign_investment.csv",show_col_types = FALSE)

# Outputs:
mean_years_in_school <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/mean_years_in_school.csv",show_col_types = FALSE)
life_expectancy <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/life_expectancy.csv",show_col_types = FALSE)
income <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/income.csv",show_col_types = FALSE)
income_share_20 <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/income_share_20.csv",show_col_types = FALSE)
murder <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/murder.csv",show_col_types = FALSE)
```

In the next part we will adapt all data sets accordingly

## Merge data

```{r}

```


## Adjustmenr of data

### Material footprint
Material footprint is an input.We define, that the material foortprint needs to be as small as possible in order to be optimal. 
```{r}
glimpse(material_footprint)
```
```{r}
min(material_footprint$value)
```
All values are above 0. The direction of the data is also correct.

### CO2
CO2 is an input. The less CO2 emissions, the better.
```{r}
min(CO2$value, na.rm = TRUE)
```
CO2 has values of 0.
```{r}
check0(CO2$value)
```








