---
title: "Bachelor's Thesis"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

# Data Preparation

## What data sets to use

Input:

* CO2 Emissions per person
* women in parliament
* democracy
* mean years in school -> data on gapminder only until 2009

Output:
* life expactancy
* income
* murder rate
* employment rate


## install packages

```{r}
# install.packages("tidyverse")
# install.packages("deaR")
# tinytex::install_tinytex()
# install.packages('countrycode')
```


## load libaries

```{r}
library(tidyverse)
library(deaR)
library(ggplot2)
library(countrycode)
```


## load data

```{r}

# Input
co2 <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/co2_emissions_tonnes_per_person.csv",show_col_types = FALSE)
women_in_parliament <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/percentage_women_in_parliament.csv",show_col_types = FALSE)
democracy <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/demox_eiu.csv",show_col_types = FALSE)
# mean_years_in_school_men <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/mean_years_in_school_men_25_years_and_older.csv",show_col_types = FALSE)
# mean_years_in_school_women <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/mean_years_in_school_women_25_years_and_older.csv",show_col_types = FALSE)

# Output
life_expactancy <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/life_expectancy_years.csv",show_col_types = FALSE)
income <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/income_per_person_gdppercapita_ppp_inflation_adjusted.csv",show_col_types = FALSE)
murder <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/murder_per_100000_people.csv",show_col_types = FALSE)
employment_rate <- read_csv("G:/My Drive/Bildung/Hochschule/BA/Data/gapminder/aged_15plus_employment_rate_percent.csv",show_col_types = FALSE)

```


## Choose year with biggest overlap


## Extract columns of chosen year

```{r}

# Input
co2_2014 <- co2[c("country","2014")]
wip_2014 <- women_in_parliament[c("country","2014")]
democracy_2014 <- democracy[c("country","2014")]
# school_men_2014 <- mean_years_in_school_men[c("country","2014")]
# school_women_2014 <- mean_years_in_school_women[c("country","2014")]

# Output
life_expactancy_2014 <- life_expactancy[c("country","2014")]
income_2014 <- income[c("country","2014")]
murder_2014 <- murder[c("country","2014")]
employment_2014 <- employment_rate[c("country","2014")]

```

## Remove Ks, Ms, etc... and make it numerical

```{r}

income_2014$`2014` <- as.numeric(gsub("k", "e3", income_2014$`2014`))/1000 # divided by 1000 to avoid different orders of magnitude within dataset

```

## Merge data frames and drop countries with NA

```{r}

# Create list of all data frames
list_all_data <- list(
  co2_2014, 
  wip_2014, 
  democracy_2014, 
  # school_men_2014, 
  # school_women_2014, 
  life_expactancy_2014, 
  income_2014, 
  murder_2014, 
  employment_2014)


# Merge all data frame together by the country attribute
final <- list_all_data %>% reduce(full_join, by="country")


# Change column names to something meaningful
colnames(final) <- c(
  "country", 
  "co2_2014", 
  "wip_2014", 
  "democracy_2014", 
  # "school_men_2014", 
  # "school_women_2014", 
  "life_expactancy_2014", 
  "income_2014", 
  "murder_2014", 
  "employment_2014")

# convert tibble to data frame
final <- as.data.frame(final)

# Remove countries with NA values
final <- drop_na(final)

head(final)

```

## Save result as csv

```{r}

write_csv(final, "G:/My Drive/Bildung/Hochschule/BA/Data/Results/country_data.csv")

```


# DEA


## DEA preparation

```{r}

# Documentation: https://cran.r-project.org/web/packages/deaR/deaR.pdf

# Number of in- and outputs
number_of_inputs <- 3
number_of_outputs <- 4

orientation <- "io" 
# io: input oriented
# oo: output oriented

return_to_scale <- "vrs"
# crs: constant return to scale
# vrs: variable return to scale
# nirs: non-increasing
# ndrs: non-decreasing
# grs: generalized


model_data <- read_data(final, ni=number_of_inputs, no=number_of_outputs, dmus = 1)


result <- model_basic(model_data, orientation = orientation, rts=return_to_scale)

## Warning: There are data with very different orders of magnitude. Try to re-define the units of measure or some linear problems may be ill-posed.

```


## Results

### Efficiencies

```{r}

eff <- efficiencies(result)

```


### Targets

```{r}

# Get targets
targets <- as.data.frame(targets(result))

```


```{r}

# Add efficiency to final data frame
final$eff <- as.vector(eff)

```


```{r}

# Combine final and targets
final <- cbind(final, targets)

# remove rownames
rownames(final) <- NULL




```


```{r}

# add continent
final$continent <- countrycode(sourcevar = final$country,
                               origin = "country.name",
                               destination = "continent")

head(final)

```

```{r}

write_csv(final, "G:/My Drive/Bildung/Hochschule/BA/Data/Results/dea_results.csv")

```



### Visualization

```{r}

# Plot no. 1
final %>%
  ggplot(aes(country, co2_2014))+
  geom_bar(stat="identity",
           position = position_dodge(width = 0.1),
           width=0.8,
           aes(fill=wip_2014))+
  theme(axis.text.x = element_text(angle = 90, hjust=0.95))+
  coord_flip()


```

```{r}

# Plot no. 2
final %>%
  ggplot(aes(eff, co2_2014))+
  geom_point(alpha = 0.5,
             size = 3,
             aes(color = continent))+
  geom_text(size = 2,
            aes(label=country))


```

```{r}

final %>%
  ggplot(aes(co2_2014, income_2014))+
  geom_point()+
  geom_smooth(method="lm")

```

```{r}

df1 <- data.frame(final$co2_2014, final$target_input.co2_2014, final$country)
head(df1)

```



```{r}

df1_long <- df1 %>%
  gather("Stat", "Value", -final.country)
head(df1_long)

```

```{r}

df1_long %>%
  ggplot(aes(x = final.country, y = Value, fill = Stat)) +
  geom_col(position = "dodge")+
  coord_flip()

```



```{r}


```





