---
title: "BA - DEA"
output: html_notebook
---

# load libraries

```{r}
library(tidyverse)
library(deaR)
library(ggplot2)
library(countrycode)

source("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/code/functions.R")
```

Country groups

```{r}
regions <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/regions.csv", show_col_types = FALSE)

Africa <- regions$country[regions$continent == "Africa"]
Europe <- regions$country[regions$continent == "Europe"]
Americas <- regions$country[regions$continent == "Americas"]
Asia <- regions$country[regions$continent == "Asia"]
Oceania <- regions$country[regions$continent == "Oceania"]
EU <- regions$country[regions$EU == TRUE]
OECD <- regions$country[regions$OECD == TRUE]
Selection_01 <- regions$country[regions$selection_01 == TRUE]

```

# Preparation

## Select data to be used and set parameter

```{r}
# Chose the attempt
attempt = 113

# Number of in- and outputs -> checl struture of selected data set!
number_of_inputs <- 4
number_of_outputs <- 5

# location of inputs and outputs
input_cols <- c()
output_cols <- c()

# only from 1990?
from_1990 <- "no"

# only one year?
only_one_year <- 0 # 0 means no

# onyl specified chosen_countries?
chosen_countries <- c() # enter a vector with strings; empty means all

orient <- "io"
# io: input oriented
# oo: output oriented

return_to_scale <- "vrs"
# crs: constant return to scale
# vrs: variable return to scale
# nirs: non-increasing
# ndrs: non-decreasing
# grs: generalized
```

### Load data

```{r}
data = read_final(attempt)
str(data)
```

### Split dmu column into country and year (for filtering)

```{r}
data <- separate(data, dmu, c("country", "year"), "_", remove=FALSE)
```

### Apply chosen selection

```{r}

if (from_1990 != "no") {
  data <- data %>%
    filter(year >= 1990)
}

if (only_one_year != 0) {
  data <- data %>%
    filter(year == only_one_year)
}

if (!is.null(chosen_countries)) {
  data <- data %>%
    filter(country %in% chosen_countries)
}
  
```

### Delete country and year column

```{r}
data$country <- NULL
data$year <- NULL
data <- data %>% relocate(dmu)
```

# DEA

```{r}
# Documentation: https://cran.r-project.org/web/packages/deaR/deaR.pdf

if (length(input_cols) == 0) {
  model_data <- read_data(data, 
                        ni=number_of_inputs, 
                        no=number_of_outputs, 
                        dmus = 1)
  
} else {
  model_data <- read_data(data, 
                        ni=number_of_inputs, 
                        no=number_of_outputs, 
                        inputs=input_cols,
                        outputs=output_cols,
                        dmus = 1)
}


result <- model_basic(model_data, orientation = orient, rts=return_to_scale)
```

## Efficiencies and Targets

```{r}
# Efficiencies
eff <- as.data.frame(efficiencies(result))
# add column for dmu names
eff$dmu <- rownames(eff)
# delete rownames
rownames(eff) <- NULL
# Rename efficiency column
colnames(eff)[1] <- "efficiencies"

# get targets
targets <- as.data.frame(targets(result))
# add column for dmu names
targets$dmu <- rownames(targets)
# delte rownames
rownames(targets) <- NULL
```

## Merge all together

```{r}
data_and_results <- list(
  data,
  eff,
  targets
)

data_dea <- data_and_results %>% reduce(full_join, by="dmu")
```

```{r}
data_dea <- data_dea %>% relocate(efficiencies, .after = dmu)
```

## Split um dmu column to country and year but keep dmu column

```{r}
data_dea <- separate(data_dea, dmu, c("country", "year"), "_", remove=FALSE)
```

## Add continents

```{r}
data_dea$continent <- countrycode(sourcevar = data_dea$country,
                               origin = "country.name",
                               destination = "continent")
```

## export as csv

create name for the file

```{r}
filename <- paste(as.character(attempt), "_", orient, "_", return_to_scale, sep = "")

if (from_1990 != "no") {
  filename <- paste(filename, "_", "from1990", sep = "")
}

if (only_one_year != 0) {
  filename <- paste(filename, "_", as.character(only_one_year), sep = "")  
}

if (!is.null(chosen_countries)) {
  if (is_empty(setdiff(Europe, chosen_countries))) {
    filename <- paste(filename, "_", "Europe", sep = "")
  } else if (is_empty(setdiff(Americas, chosen_countries))) {
    filename <- paste(filename, "_", "Americas", sep = "")
  } else if (is_empty(setdiff(EU, chosen_countries))) {
    filename <- paste(filename, "_", "EU", sep = "")
  } else if (is_empty(setdiff(Africa, chosen_countries))) {
    filename <- paste(filename, "_", "Africa", sep = "")
  } else if (is_empty(setdiff(Asia, chosen_countries))) {
    filename <- paste(filename, "_", "Asia", sep = "")
  } else if (is_empty(setdiff(Selection_01, chosen_countries))) {
    filename <- paste(filename, "_", "Selection_01", sep = "")
  } else if (length(chosen_countries) == 1) {
    filename <- paste(filename, "_", as.character(chosen_countries[1]), sep = "")
  } else {
    filename <- paste(filename, "_", "notAllCountries", sep = "")
  }
}
```

```{r}
write_csv(data_dea, paste("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/dea_results_", filename, ".csv", sep = ""))
```

## 1on1 DEA

```{r}
for (i in 1:number_of_inputs) {
  for (j in 1:number_of_outputs) {
    
    partial_data <- data[c(1,1+i,number_of_inputs+1+j)]
    
    model_data <- read_data(partial_data,
                        ni=1,
                        no=1,
                        dmus = 1)

    result <- model_basic(model_data, orientation = orient, rts=return_to_scale)


# Efficiencies
    eff <- as.data.frame(efficiencies(result))

# add column for dmu names
    eff$dmu <- rownames(eff)

# delete rownames
    rownames(eff) <- NULL

# Rename efficiency column
    colnames(eff)[1] <- "efficiencies"

# get targets
    # targets <- as.data.frame(targets(result))

# add column for dmu names
    # targets$dmu <- rownames(targets)

# delte rownames
    # rownames(targets) <- NULL

    data_and_results <- list(
      partial_data,
      eff
    )

    data_dea <- data_and_results %>% reduce(full_join, by="dmu")

    data_dea <- data_dea %>% relocate(efficiencies, .after = dmu)

    data_dea <- separate(data_dea, dmu, c("country", "year"), "_", remove=FALSE)

    write_csv(data_dea, paste("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/dea_results_", filename, "_", as.character(i), as.character(j), ".csv", sep = ""))

  }

}
```
