---
title: "BA - data preparation - 2"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

# Preparation of the chosen data sets

The chosen inputs are:

-   CO2

-   material footprint

-   government debts

-   foreign direct investment

The chosen outputs are

-   life expectancy

-   income

-   mean years of schooling

-   murder rate

-   income share of lowest 20 percent

Both inputs and output data sets need to be adjusted according to the
input oriented DEA. Inputs should be minimized, outputs should be
maximized to achieve optimal results. Also, all data must be strictly
positive.

```{r}
library(tidyverse) 

source("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/code/functions.R")
```

## Load data

```{r}
data <- read_final(12)
str(data)
```

In the next part we will adapt all data sets accordingly

### Material footprint

Material footprint is an input.We define, that the material footprint
needs to be as small as possible in order to be optimal.

```{r}
glimpse(data$material_footprint)
```

```{r}
min(data$material_footprint)
```

All values are above 0. The direction of the data is also correct.

### CO2

CO2 is an input. The less CO2 emissions, the better.

```{r}
min(data$CO2, na.rm = TRUE)
```

CO2 has no values of 0.

```{r}
check0(CO2$value)
```

### Foreign direct investment

The more foreign direct investment, the better. As it says the more the
better we need to adapt the scale to achieve the less the better

```{r}
min(data$foreign_investment)
max(data$foreign_investment)
```

Also, the data includes values of 0 and below. We need to deal with both
the negative values as well as the direction of the data set. The
minimum values is -57.5 (Luxembourg 2007), the maximum value 449 (Malta
2007)

**Handling of negative values**

In order to get only positive values, I will add 57.4 to each value.

```{r}
# data$foreign_investment <- data$foreign_investment + 57.4
```

**Handling of direction**

Inputs must follow the direction of the less the better. I will mirror
each value along the middle between min and max

```{r}
# mirror <- (max(data$foreign_investment) - min(data$foreign_investment)) / 2 # = 253.25
# 
# data$foreign_investment <- mirror + (mirror - data$foreign_investment)

# data$foreign_investment <- (data$foreign_investment - (max(data$foreign_investment)+1)) * (-1)

data$foreign_investment <- (data$foreign_investment - (min(data$foreign_investment))+1)
```

### Government debts

The less the better \<- good

No entry 0 or less :)

### Life expectancy

The more the better \<- Already fits the model

It cannot be below 0. No adjustment needed

### Income

The more the better \<- Already fits

It cannot be below 0. No adjustment needed

### Income of lowest 20 percent

The more the better \<- good

Cannot be 0

### Mean years of schooling

The more the better \<- perfect

It cannot be below 0. No adjustment needed

### Murder rate

The lower the better \<- needs to be adjusted

**Handling of direction**

This data shows the amount of murders per 100k people. To adjust the
direction of the data I will simply use the No-murder rate :) As the
numbers will be very high I will divide them by 1000

```{r}
data$murder <- (100000 - data$murder) / 1000
```

### Income share of lowest 20 %

The higher the better \<- good

It cannot be below 0. No adjustment needed

## Export adjusted data set

```{r}
final_112 <- data

write_final(final_112)

```
