---
title: "BA - Visualization"
output: html_notebook
---

## load libraries and other stuff

```{r}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(factoextra)
library(countrycode)

source("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/code/functions.R")

regions <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/regions.csv", show_col_types = FALSE)

Africa <- regions$country[regions$continent == "Africa"]
Europe <- regions$country[regions$continent == "Europe"]
Americas <- regions$country[regions$continent == "Americas"]
Asia <- regions$country[regions$continent == "Asia"]
Oceania <- regions$country[regions$continent == "Oceania"]
EU <- regions$country[regions$EU == TRUE]
OECD <- regions$country[regions$OECD == TRUE]
```

## load data

```{r}
filename_vrs <- "dea_results_113_io_vrs.csv"
filename_crs <- "dea_results_113_io_crs.csv"

data_vrs <- read_csv(paste("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/", filename_vrs, sep = ""), show_col_types = FALSE)
data_crs <- read_csv(paste("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/", filename_crs, sep = ""), show_col_types = FALSE)
```

## Some stats

```{r}
summary(data_vrs)
```

```{r}
summary(data_crs)
```

## Problems

at first sight

-   target non-murder rate above 100 in crs data set

-   target mean years in school sometimes ridiculously high

-   Same goes for life expectancy

# Preparation of several tables

## Recalculate foreign investment columns

```{r}
# mirror = 253.25
# 
# data_crs$foreign_investment <- 2 * mirror - data_crs$foreign_investment - 57.4
# data_crs$target_input.foreign_investment <- 2 * mirror - data_crs$target_input.foreign_investment - 57.4
# 
# data_vrs$foreign_investment <- 2 * mirror - data_vrs$foreign_investment - 57.4
# data_vrs$target_input.foreign_investment <- 2 * mirror - data_vrs$target_input.foreign_investment - 57.4

# # crs
# data_crs$foreign_investment <- (data_crs$foreign_investment * (-1)) + 450
# 
# data_crs$target_input.foreign_investment <- data_crs$target_input.foreign_investment * (-1) + 450
# 
# # vrs
# data_vrs$foreign_investment <- (data_vrs$foreign_investment * (-1)) + 450
# 
# data_vrs$target_input.foreign_investment <- data_vrs$target_input.foreign_investment * (-1) + 450

# # crs
# data_crs$foreign_investment <- data_crs$foreign_investment - 58.5
# 
# data_crs$target_input.foreign_investment <- data_crs$target_input.foreign_investment - 58.5
# 
# # vrs
# data_vrs$foreign_investment <- data_vrs$foreign_investment - 58.5
# 
# data_vrs$target_input.foreign_investment <- data_vrs$target_input.foreign_investment - 58.5
```

## CRS-VRS general data set

Excluding target values

```{r}
data_general <- merge( data_crs %>% 
                         rename(efficiency_crs = efficiencies) %>% 
                         select(dmu, country, ,continent, year, efficiency_crs, CO2, material_footprint, foreign_investment, government_debt,life_expectancy, income, mean_years_in_school, murder, income_share_20), 
                       data_vrs %>% 
                         rename(efficiency_vrs = efficiencies) %>% 
                         select(dmu, efficiency_vrs),
                       by = "dmu") %>%
  relocate(efficiency_vrs, .after = efficiency_crs)
```

## Add ranks

```{r}
data_general <- data_general %>% 
  mutate(rank_crs = min_rank(desc(efficiency_crs)),
         rank_vrs = min_rank(desc(efficiency_vrs))) %>%
  relocate(rank_crs, .after = efficiency_vrs) %>%
  relocate(rank_vrs, .after = rank_crs)
```

## New table: Countries vs. years

```{r}
#CRS
data_crs_wider_rank <- data_general[c("country", "year", "rank_crs")] %>% pivot_wider(names_from = year, values_from = rank_crs)

data_crs_wider_rank <- data_crs_wider_rank[c("country", as.character(c(1990:2016)))]


data_crs_wider_eff <- data_general[c("country", "year", "efficiency_crs")] %>% pivot_wider(names_from = year, values_from = efficiency_crs)

data_crs_wider_eff <- data_crs_wider_eff[c("country", as.character(c(1990:2016)))]



# VRS
data_vrs_wider_rank <- data_general[c("country", "year", "rank_vrs")] %>% pivot_wider(names_from = year, values_from = rank_vrs)

data_vrs_wider_rank <- data_vrs_wider_rank[c("country", as.character(c(1990:2016)))]



data_vrs_wider_eff <- data_general[c("country", "year", "efficiency_vrs")] %>% pivot_wider(names_from = year, values_from = efficiency_vrs)

data_vrs_wider_eff <- data_vrs_wider_eff[c("country", as.character(c(1990:2016)))]
```

## Normalize efficiency

Germany 1991 as basis

```{r}
data_crs_normal <- data_crs
data_crs_normal["efficiencies"] <- data_crs_normal["efficiencies"] / as.numeric(filter(data_crs, dmu == "Germany_1991")["efficiencies"])
```

## Well-being indicator data set

```{r}
# GDP
wellfare_ind <- data_general %>%
  select(dmu, country, continent, efficiency_crs, efficiency_vrs, income)

# HDI
hdi <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/hdi.csv", show_col_types = FALSE)

wellfare_ind <- merge(wellfare_ind, hdi, by = "dmu", all.x = TRUE)

colnames(wellfare_ind)[ncol(wellfare_ind)] <- "hdi"

#HPI
hpi <- read_csv("D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/raw_data/preprocessed_data/hpi.csv", show_col_types = FALSE)

wellfare_ind <- merge(wellfare_ind, hpi, by = "dmu", all.x = TRUE)

colnames(wellfare_ind)[ncol(wellfare_ind)] <- "hpi"
```

# Exploratory Analyses

## Means and variance

### Means per country

```{r}
means_country <- data_general %>%
  select(-dmu, -continent, -year, -rank_crs, -rank_vrs) %>%
  group_by(country) %>%
  summarize(across(everything(), mean))
  
```

### Variance per country

```{r}
variance_country <- data_general %>%
  select(-dmu, -continent, -year, -rank_crs, -rank_vrs) %>%
  group_by(country) %>%
  summarize(across(everything(), var))

```

Check if variance greater than mean

```{r}
variance_country > means_country
```

Especially foreign investment and government debt mean cannot be used. The income column also shows some TRUE values.

### Means per year

```{r}
means_year <- data_general %>%
  select(-dmu, -continent, -country, -rank_crs, -rank_vrs) %>%
  group_by(year) %>%
  summarize(across(everything(), mean))
```

Visualization of average development over time

```{r}
means_year %>%
  pivot_longer(cols = c("efficiency_crs", "efficiency_vrs", "CO2", "material_footprint", "foreign_investment", "government_debt", "life_expectancy", "income", "mean_years_in_school", "murder", "income_share_20"), names_to = "indicator") %>%
  ggplot(aes(year, value))+
  geom_line()+
  facet_wrap(vars(indicator), scales = "free_y")
```

CO2 emissions per person have been decreasing since the 00s.

Mean years in school have been increasing

Average efficiencies higher in the the 90s than in nowdays, but rising again? Why??

### Variance per year

```{r}
variance_year <- data_general %>%
  select(-dmu, -continent, -country, -rank_crs, -rank_vrs) %>%
  group_by(year) %>%
  summarize(across(everything(), var))
```

```{r}
variance_year %>%
  pivot_longer(cols = c("efficiency_crs", "efficiency_vrs", "CO2", "material_footprint", "foreign_investment", "government_debt", "life_expectancy", "income", "mean_years_in_school", "murder", "income_share_20"), names_to = "indicator") %>%
  ggplot(aes(year, value))+
  geom_line()+
  facet_wrap(vars(indicator), scales = "free_y")
```

Variance over year too big -\> we cannot use the means per year data

### Add average efficiency to wide data frames

```{r}
# avererage efficiencies for crs data set
crs_eff <- data_crs[c("country", "efficiencies")] %>%
  group_by(country) %>%
  summarise(across(everything(), mean))

# merge efficienies and wide crs rank data set
data_crs_wider_rank <- merge(data_crs_wider_rank, crs_eff, by = "country")
data_crs_wider_rank <- data_crs_wider_rank %>% relocate(efficiencies, .after = country)
colnames(data_crs_wider_rank)[2] <- "average_efficiency"

# add rank based on average efficiencies
data_crs_wider_rank <- data_crs_wider_rank %>% mutate(rank = min_rank(desc(average_efficiency)))
data_crs_wider_rank <- data_crs_wider_rank %>% relocate(rank)

# merge efficienies and wide crs efficiency data set
data_crs_wider_eff <- merge(data_crs_wider_eff, crs_eff, by = "country")
data_crs_wider_eff <- data_crs_wider_eff %>% relocate(efficiencies, .after = country)
colnames(data_crs_wider_eff)[2] <- "average_efficiency"

# add rank based on average efficiencies
data_crs_wider_eff <- data_crs_wider_eff %>% mutate(rank = min_rank(desc(average_efficiency)))
data_crs_wider_eff <- data_crs_wider_eff %>% relocate(rank)



# avererage efficiencies for vrs data set
vrs_eff <- data_vrs[c("country", "efficiencies")] %>%
  group_by(country) %>%
  summarise(across(everything(), mean))

# merge efficienies and wide vrs rank data set
data_vrs_wider_rank <- merge(data_vrs_wider_rank, vrs_eff, by = "country")
data_vrs_wider_rank <- data_vrs_wider_rank %>% relocate(efficiencies, .after = country)
colnames(data_vrs_wider_rank)[2] <- "average_efficiency"

# add rank based on average efficiencies
data_vrs_wider_rank <- data_vrs_wider_rank %>% mutate(rank = min_rank(desc(average_efficiency)))
data_vrs_wider_rank <- data_vrs_wider_rank %>% relocate(rank)

# merge efficienies and wide vrs efficiency data set
data_vrs_wider_eff <- merge(data_vrs_wider_eff, vrs_eff, by = "country")
data_vrs_wider_eff <- data_vrs_wider_eff %>% relocate(efficiencies, .after = country)
colnames(data_vrs_wider_eff)[2] <- "average_efficiency"

# add rank based on average efficiencies
data_vrs_wider_eff <- data_vrs_wider_eff %>% mutate(rank = min_rank(desc(average_efficiency)))
data_vrs_wider_eff <- data_vrs_wider_eff %>% relocate(rank)
```

## PCA

```{r}
# PCA -------
pca <- prcomp(data_general[,9:ncol(data_general)], scale = TRUE)
pca
summary(pca)
# -> die ersten 6 PCs stellen 90 Prozent dar
plot(pca, tpye = "l")
biplot(pca, scale = 0)

# EXTRACT PC SCORES ------
str(pca)
pca$x

data_general2 <- cbind(data_general, pca$x[,1:2])

# CORRELATION
cor(data_general[,9:ncol(data_general)], pca$x)

```

> In PC1 most influencial factors (all positive)
>
> 1.  income
> 2.  material footprint
> 3.  life expectancy
> 4.  CO2
> 5.  mean years in school
> 6.  murder
>
> In PC2:
>
> 1.  government debt (+)

## Clustering

### Clustering of all DMUs

```{r}
data.lables <- data_general$dmu

data_scale <- scale(data_general[,9:ncol(data_general)])

# How many cluster do we need?
fviz_nbclust(data_scale, kmeans, method = "wss")
```

It is difficult to make out the ideal number of cluster but 6 seems to be one of the better options.

```{r}
km.out <- kmeans(data_scale, centers = 5, nstart = 100)
# print(km.out)
```

```{r}
km.clusters <- km.out$cluster
rownames(data_scale) <- data.lables
fviz_cluster(list(data=data_scale, cluster=km.clusters))
```

```{r}
data_general$cluster <- km.clusters
relocate(data_general, cluster, .after = continent)
```

What countries are in the cluster?

```{r}
cluster_country <- data_general %>%
  group_by(cluster)%>%
  summarize(unique_countries = unique(country))

cluster_1 <- cluster_country %>%
  filter(cluster == 1) %>%
  select(unique_countries)

cluster_2 <- cluster_country %>%
  filter(cluster == 2) %>%
  select(unique_countries)

cluster_3 <- cluster_country %>%
  filter(cluster == 3) %>%
  select(unique_countries)

cluster_4 <- cluster_country %>%
  filter(cluster == 4) %>%
  select(unique_countries)

cluster_5 <- cluster_country %>%
  filter(cluster == 5) %>%
  select(unique_countries)

cluster_6 <- cluster_country %>%
  filter(cluster == 6) %>%
  select(unique_countries)
```

```{r}
cluster_ind_info_mean <- data_general %>%
  select(CO2, material_footprint, foreign_investment, government_debt, life_expectancy, income, mean_years_in_school, murder, income_share_20, cluster) %>%
  group_by(cluster) %>%
  summarise_all(mean)

write_csv(cluster_ind_info_mean, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/cluster_ind_info_mean.csv")

cluster_ind_info_var <- data_general %>%
  select(CO2, material_footprint, foreign_investment, government_debt, life_expectancy, income, mean_years_in_school, murder, income_share_20, cluster) %>%
  group_by(cluster) %>%
  summarise_all(var)

write_csv(cluster_ind_info_var, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/cluster_ind_info_var.csv")
```

```{r}
data_general %>%
  select(CO2, material_footprint, foreign_investment, government_debt, life_expectancy, income, mean_years_in_school, murder, income_share_20, cluster) %>%
  pivot_longer(cols = c("CO2", "material_footprint", "foreign_investment", "government_debt", "life_expectancy", "income", "mean_years_in_school", "murder", "income_share_20"), names_to = "indicator") %>%
  ggplot(aes(indicator, value)) +
  geom_boxplot()+
  geom_jitter(width = 0.1,
              alpha = 0.5,
              )
```

### Clustering of average country values

```{r}
data.lables_mean <- means_country$country

data_scale_mean <- scale(means_country[4:ncol(means_country)])

# How many cluster do we need?
fviz_nbclust(data_scale_mean, kmeans, method = "wss")
```

3 clusters makes the most sense

```{r}
km.out_mean <- kmeans(data_scale_mean, centers = 4, nstart = 100)
# print(km.out)

km.clusters_mean <- km.out_mean$cluster
rownames(data_scale_mean) <- data.lables_mean
p<- fviz_cluster(list(data=data_scale_mean, cluster=km.clusters_mean))
p
```

```{r}
pca_analyse <- prcomp(data_scale_mean, rank =4)
pca_analyse$rotation[,1:4]
#?prcomp


```

## Correlation between GDP and other factors

### Input factors

```{r}
cor(data_general$income, data_general$CO2) # / 0.62
```

-\> strong correlations

```{r}
cor(data_general$income, data_general$foreign_investment) # / 0.40
```

```{r}
cor(data_general$income, data_general$mean_years_in_school) # / 0.41
```

```{r}
cor(data_general$income, data_general$material_footprint) # / 0.84
```

-\> strong correlation

### Other well-begin factors

```{r}
cor(wellfare_ind$income, wellfare_ind$hdi, use = "pairwise.complete.obs") # / 0.97
cor(wellfare_ind$income, wellfare_ind$hpi, use = "pairwise.complete.obs") # / -0.08

```

## Add clusters to wellfare_ind data set

```{r}
# Adding more data to data set for grouping
# Cluster
wellfare_ind <- merge(wellfare_ind, data_general[c("dmu", "cluster")])

wellfare_ind$cluster <- factor(wellfare_ind$cluster)

# Average
avg_wellfare_ind <- wellfare_ind %>%
  select(country, efficiency_crs, efficiency_vrs, hdi, hpi, income) %>%
  group_by(country) %>%
  summarize(across(everything(), mean)) %>%
  mutate(cluster = as.character(km.clusters_mean))

avg_wellfare_ind$continent <- countrycode(sourcevar = avg_wellfare_ind$country,
                               origin = "country.name",
                               destination = "continent")
```

# Export data sets for further analysis

```{r}
# general data sets
write_csv(data_general, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/data_general.csv")

write_csv(wellfare_ind, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/wellfare_ind.csv")

write_csv(avg_wellfare_ind, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/avg_wellfare_ind.csv")


# means and variance
write_csv(means_country, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/means_country.csv")

write_csv(means_year, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/means_year.csv")

write_csv(variance_country, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/variance_country.csv")

write_csv(variance_year, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/variance_year.csv")


# wide data sets
write_csv(data_crs_wider_eff, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/data_crs_wider_eff.csv")

write_csv(data_crs_wider_rank, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/data_crs_wider_rank.csv")

write_csv(data_vrs_wider_eff, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/data_vrs_wider_eff.csv")

write_csv(data_vrs_wider_rank, "D:/Daten/Bildung/HS Mannheim/BA/bachelors-thesis/processed_data/Working Files/data_vrs_wider_rank.csv")

```
